---
title: "Introduction to StatComp22086"
author: "sa22204143"
date: "2022/12/7"
output: rmarkdown::html_vignette
vignette: >
 %\VignetteIndexEntry{Introduction to StatComp22086}
 %\VignetteEngine{knitr::rmarkdown}
 %\VignetteEncoding{UTF-8}
---

## Overview

_StatComp22086_ is a simple R package includes three functions. 'beta_update' Update the parameters (Coordinate descent method). 'SPCA' The function of SPCA method. Output parameters: loadings(loading obtained by SPCA method), pev(the proportion of variance explained by the principal component), cumsum_pev(the cumulative proportion of variance explained by the principal component). 'EMC' EM method of certain case. We only know that Xi's have distribution Exp(a)(i.i.d) and Xi falls in (ui,vi) for i=1,...,n. This function can use to get the unknown parameter a. 

## beta_update

```{r}
beta_update <- function(x, y, beta, lambda, lambda0){    
  beta0 <- matrix(1, nrow(beta), 1)
  while(max(abs(beta - beta0)) > 1e-3){
    beta0 <- beta
    for (j in 1:nrow(beta)){   
      temp <- rep(0,nrow(y))
      for (i in 1:nrow(y)){
        temp[i] <- y[i] - sum(beta*x[,i])+beta[j]*x[j,i]
      }
      ru <- sum(x[j,]*temp)
      z <- sum((x^2)[j,]) + 2*lambda0
      if (ru < (-lambda/2)){  
        beta[j] <- ((ru + (lambda/2))/z)
      }else if((ru > (lambda/2))){
        beta[j] <- ((ru - (lambda/2))/z)
      }else{
        beta[j] <- 0
      }    
    }
  }
  return(beta)
}
```

## SPCA

```{r}
SPCA <- function(cormat, k, eps, lambda, lambda1){
  x.eigen <- eigen(cormat)
  d <- x.eigen$values
  d <- (d + abs(d))/2
  v <- x.eigen$vectors
  x <- v %*% diag(sqrt(d)) %*% t(v)
  n <- nrow(x)
  p <- ncol(x)
  V <- svd(x)$v
  alpha <- V[,1:k]    
  
  Beta_now <- matrix(0, nrow=p, ncol=k)
  Beta_new <- matrix(1.1, nrow=p, ncol=k)
  iter <- 0
  while(max(abs((Beta_new)-(Beta_now)))>eps){
    iter <- iter+1
    Beta_now <- Beta_new
    for (j in 1:k){
      y <- drop(x%*%alpha[,j])
      Beta_new[,j] <- beta_update(as.matrix(x), as.matrix(y), as.matrix(Beta_new[,j]), lambda1[j], lambda)
    }
    tempp <- svd(cormat%*%Beta_new)
    alpha <- (tempp$u)%*%t(tempp$v)    
  }
  normbeta <- sqrt(apply(Beta_new^2, 2, sum))
  normbeta[normbeta==0] <- 1
  beta <- t(t(Beta_new)/normbeta)   
  u <- x%*%beta
  R <- qr.R(qr(u))
  
  pev <- diag(R^2)/sum((svd(x)$d)^2)
  vn <- dimnames(x)[[2]]
  obj <- list(loadings = beta, pev = pev,cumsum_pev = cumsum(pev))
  return(obj)
}

```

```{r eval=FALSE}
library(elasticnet)
data(pitprops)
SPCA(pitprops,6,1e-6,0,c(0.06,0.16,0.1,0.5,0.5,0.5))
```

## EMC


```{Rcpp}
#include <Rcpp.h>
using namespace Rcpp;

// [[Rcpp::export]]
double EMC(double lambda1, double lambda2, NumericVector u, NumericVector v){
  double eps = pow(10,-5);
  int n = sizeof(u);
  while(abs(lambda1-lambda2)>=eps){
    lambda1 = lambda2;
    NumericVector x = exp(-lambda1*u);
    NumericVector y = exp(-lambda1*v);
    lambda2 = n/sum(((lambda1*u+1)*x-(lambda1*v+1)*y)/(lambda1*(x-y)));
  }
  return(lambda2);
}
```

```{r eval=FALSE}
lambda1 <- 2
lambda2 <- 1
u <- c(11,8,27,13,16,0,23,10,24,2)
v <- c(12,9,28,14,17,1,24,11,25,3)
emc <- EMC(lambda1,lambda2,u,v)
emc
```



